---
title: "Shiny Application and Reproducible Pitch"
author: "QW"
date: "2023-06-07"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Course Project
This assignment has two parts. First, we will create a Shiny application and deploy it on Rstudio's servers. Second, we will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.


## Load R Packages
```{r}
library(leaflet)
library(shiny)
library(miniUI)
library(googleVis)
library(plotly)
library(manipulate)
library(scatterplot3d)
```

## Dataset
The dataset used in this app is mtcars, which comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models). Here is a few rows in mtcars.
```{r}
head(mtcars)
```

## Subset the data by the types of transmission and numbers of cylinders.
```{r}
# Define UI for application that draws a histogram
ui <- fluidPage(

    # Application title
    titlePanel("Motor Trend Car Road Tests Dataset (1973-74 models"),

    # Sidebar with a slider input for number of bins 
    sidebarLayout(
        sidebarPanel(
            helpText("Car Performance Evaluation:"), 
            sliderInput('disp', 'Displacement (cu.in.)', min=10, max=480, value=c(70,480), step=10), 
            sliderInput('hp', 'Gross horsepower', min=100, max=340, value=c(100,340), step=10), 
            checkboxGroupInput('am', 'Transmission:', c("Automatic"=0, "Manual"=1), selected = c(0,1)),
            checkboxGroupInput('cyl', 'Number of Cylinders:', c("4"=4, "6"=6, "8"=8), selected = c(4,6,8))
        ),

        # Show a plot of the generated distribution
        mainPanel(
            dataTableOutput('table') 
        )
    )
)

# Define server logic required to draw a histogram
server <- function(input, output) {

    output$table <- renderDataTable({
        disp_seq <- seq(from = input$disp[1], to = input$disp[2], by = 0.1)
        hp_seq <- seq(from = input$hp[1], to = input$hp[2], by = 1)
        mydata <- transmute(mtcars, Car = rownames(mtcars),  Displacement = disp, 
                            Horsepower = hp, Transmission = am, NumCylinders = cyl) 
                             
        mydata <- filter(mydata, Displacement %in% disp_seq, Horsepower %in% hp_seq, Transmission %in% input$am, NumCylinders %in% input$cyl)
        
        mydata <- mutate(mydata, Transmission = ifelse(Transmission==0, "automatic", "manual"))
        mydata <- data.frame(mydata)
        mydata
        
    })
}

# Run the application 
shinyApp(ui = ui, server = server)
```

## Using this apps, you can have a brief picture about these automobile designs during the 1970 period time, by selecting the parameters you're interested in. Thank you!
